A Bayesian method for inference of fundamental stellar parameters

### 2013-10-16 paper/paper.tex
Working marginalization, test to odyssey

@@

>>>>

\section{Introduction}

Other methods of stellar parameter inference: SPC\citep{blj+12}, MOOG, SME \citep{vp96}.

@@

\subsection{Sampling with emcee}
Citation to DFM \citep{fhl+12}, GW \citep{gw10}, and CosmoHAMMER \citep{asa+13}.

\section{Validation tests}
Comparison to main sequence stars of HAT-P-9, and WASP-14, from the TRES archive \citep{tfs+12}.

Comparisons using HIRES data?
